MCDA-EVSE

### 2024-05-19 code/MCDA-EVSE.Rmd
add electricity data

# get API Key
census_api_key(dlgInput("Enter a Census API Key", 
  Sys.getenv("CENSUS_API_KEY"))$res,
  overwrite = TRUE)

@@

```
```{r}
# add TSFCA
TSFCA <- ac(p = philly20$totalpop, 
            n = evse$num, 
            D = dist.matrix, d0 = 2000, family = "2SFCA")
philly20 <- philly20 %>% 
  mutate(TSFCA = TSFCA)
```

@@

>>>>

# get API Key
# census_api_key(dlgInput("Enter a Census API Key", 
#   Sys.getenv("CENSUS_API_KEY"))$res,
#   overwrite = TRUE)

@@

```{r}
# add TSFCA
TSFCA <- ac(p = philly20$totalpop, 
            n = evse$num, 
            D = dist.matrix, d0 = 2000, family = "2SFCA")
philly20 <- philly20 %>% 
  mutate(TSFCA = TSFCA)
```

@@

electricity <- read.csv(here("data", "raw", "property-electricity-data.csv")) %>% 
  dplyr::select(Y = y_coord, X = x_coord, portfolio_bldg_id, postal_code, primary_property_type, sector, electricity_2021) %>%
  na.omit() %>%
  st_as_sf(coords = c("X", "Y"), crs = 4326, agr = "constant") %>%
  st_transform('ESRI:102728')
